\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-26 paper/subdocuments/results.Rnw
discard/stage spielchen

<<setup_data_Brülhart_2003>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(foreign)
# Ohne Nuller
bd.0 <- read.csv("../../data/data_Schweiz_mitNull.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd.0$Jahr <- as.numeric(substr(bd.0$Veranlagungsperiode,1,4))
bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] <- bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] - 2
bd.2003<-bd.0 %.% 
  filter(Jahr==2003,Einheit=="Total")
start <- which(names(bd.2003)=="p1")
end <- which(names(bd.2003)=="p99_99")
percentile <- c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)
bd.2003<- data.frame(t(bd.2003[1,start:end]),percentile)
names(bd.2003)[1]=c("inc")
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
prob<-c(cum.p[1],diff(cum.p), .01)
freq<-3000
init<-0 
bd.2003$inc<-as.numeric(as.character(bd.2003$inc))
fin<-(abs(max(bd.2003$inc,na.rm=TRUE))+5)
ival<-c(init,bd.2003$inc,fin)
len<-10000
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
bd.2003.ind<-data.frame(s)
names(bd.2003.ind)[1]=c("inc")
bd.2003.ind$inc<-bd.2003.ind$inc/1000
@

<<setup_data_Brülhart_2010>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(foreign)
# Ohne Nuller
bd.0 <- read.csv("../../data/data_Schweiz_mitNull.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd.0$Jahr <- as.numeric(substr(bd.0$Veranlagungsperiode,1,4))
bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] <- bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] - 2
bd.2010<-bd.0 %.% 
  filter(Jahr==2010,Einheit=="Total")
start <- which(names(bd.2010)=="p1")
end <- which(names(bd.2010)=="p99_99")
percentile <- c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)
bd.2010<- data.frame(t(bd.2010[1,start:end]),percentile)
names(bd.2010)[1]=c("inc")
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
prob<-c(cum.p[1],diff(cum.p), .01)
freq<-3000
init<-0 
bd.2010$inc<-as.numeric(as.character(bd.2010$inc))
fin<-(abs(max(bd.2010$inc,na.rm=TRUE))+5)
ival<-c(init,bd.2010$inc,fin)
len<-10000
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
bd.2010.ind<-data.frame(s)
names(bd.2010.ind)[1]=c("inc")
bd.2010.ind$inc<-bd.2010.ind$inc/1000
@

@@

par(mfrow=c(1,3))
g10 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of 2003 Distribution")
title(main=paste("Overall relative density"))
abline(h=1,lty=2)
g1A <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2003 Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2003 Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

<<setup_data>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
library(reldist, quietly=TRUE, warn.conflicts = FALSE)
library(foreign)
# Get Brülhartdata for 2010
estv2010 <- read.csv("../../data/estv_normal_sonder_mitNuller_stE_2010.csv",sep=";")
###########################################
# Select percentiles for all cases (total)
estv2010.total<-estv2010[c(18:38),c(1,4)]
##
# Simulate individual data points
# cumulative probabilites
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
# probabilities
prob<-c(cum.p[1],diff(cum.p), .01)
# extreme values beyond x (to sample)
#freq<-max(normal$anz_pflichtige)
freq<-3000
init<-0
fin<-(abs(max(estv2010.total$Total,na.rm=TRUE))+5)
# generate the sequence to take pairs from
ival<-c(init,estv2010.total$Total,fin)
len<-10000 # sequence of each pair
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
estv2010.total.ind<-data.frame(s)
names(estv2010.total.ind)[1]=c("inc")
estv2010.total.ind$inc<-estv2010.total.ind$inc/1000

@@

density1 <- density(habe10$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(-70, 4600),
     ylim=c(0,1.103e-02))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(2500,2500),y=c(1.103e-02,1.103e-02))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.total.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

estv2010.married<-estv2010[c(18:38),c(1,2)]
names(estv2010.married)[2]=c("married")
##
# Simulate individual data points
# Percentile-Plot (descriptive  purpose)
# cumulative probabilites
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
# probabilities
prob<-c(cum.p[1],diff(cum.p), .01)
# extreme values beyond x (to sample)
#freq<-max(normal$anz_pflichtige)
freq<-3000
init<-0
fin<-(abs(max(estv2010.married$married,na.rm=TRUE))+5)
# generate the sequence to take pairs from
ival<-c(init,estv2010.married$married,fin)
len<-10000 # sequence of each pair
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
estv2010.married.ind<-data.frame(s)
names(estv2010.married.ind)[1]=c("inc")
estv2010.married.ind$inc<-estv2010.married.ind$inc/1000

@@

density1 <- density(habe10.married$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(-257, 8000),
     ylim=c(0,0.0101390))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(2500,2500),y=c(0.0101390,0.0101390))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.married.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

estv2010.unmarried<-estv2010[c(18:38),c(1,3)]
names(estv2010.unmarried)[2]=c("unmarried")
##
# Simulate individual data points
# Percentile-Plot (descriptive  purpose)
# cumulative probabilites
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
# probabilities
prob<-c(cum.p[1],diff(cum.p), .01)
# extreme values beyond x (to sample)
#freq<-max(normal$anz_pflichtige)
freq<-3000
init<-0
fin<-(abs(max(estv2010.unmarried$unmarried,na.rm=TRUE))+5)
# generate the sequence to take pairs from
ival<-c(init,estv2010.unmarried$unmarried,fin)
len<-10000 # sequence of each pair
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
estv2010.unmarried.ind<-data.frame(s)
names(estv2010.unmarried.ind)[1]=c("inc")
estv2010.unmarried.ind$inc<-estv2010.unmarried.ind$inc/1000

@@

density1 <- density(habe10.unmarried$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(-50, 2500),
     ylim=c(0,1.764e-02))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(1200,1200),y=c(1.764e-02,1.764e-02))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.unmarried.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

par(mfrow=c(1,3))
g10 <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of HBS Distribution")
title(main=paste("Overall relative density"))
abline(h=1,lty=2)
g1A <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

>>>>

<<setup_data_Brülhart_2003>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(foreign)
bd.0 <- read.csv("../../data/data_Schweiz_mitNull.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd.0$Jahr <- as.numeric(substr(bd.0$Veranlagungsperiode,1,4))
bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] <- bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] - 2
bd.2003<-bd.0 %.% 
  filter(Jahr==2003,Einheit=="Total")
start <- which(names(bd.2003)=="p1")
end <- which(names(bd.2003)=="p99_99")
percentile <- c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)
bd.2003<- data.frame(t(bd.2003[1,start:end]),percentile)
names(bd.2003)[1]=c("inc")
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
prob<-c(cum.p[1],diff(cum.p), 1-0.9999)
freq<-3000
init<-0 
bd.2003$inc<-as.numeric(as.character(bd.2003$inc))
fin<-(abs(max(bd.2003$inc,na.rm=TRUE))+5)
ival<-c(init,bd.2003$inc,fin)
len<-10000
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
bd.2003.ind<-data.frame(s)
names(bd.2003.ind)[1]=c("inc")
bd.2003.ind$inc<-bd.2003.ind$inc/1000
@

<<setup_data_Brülhart_2010>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(foreign)
bd.0 <- read.csv("../../data/data_Schweiz_mitNull.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd.0$Jahr <- as.numeric(substr(bd.0$Veranlagungsperiode,1,4))
bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] <- bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] - 2
bd.2010<-bd.0 %.% 
  filter(Jahr==2010,Einheit=="Total")
start <- which(names(bd.2010)=="p1")
end <- which(names(bd.2010)=="p99_99")
percentile <- c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)
bd.2010<- data.frame(t(bd.2010[1,start:end]),percentile)
names(bd.2010)[1]=c("inc")
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
prob<-c(cum.p[1],diff(cum.p), 1-0.9999)
freq<-3000
init<-0 
bd.2010$inc<-as.numeric(as.character(bd.2010$inc))
fin<-(abs(max(bd.2010$inc,na.rm=TRUE))+5)
ival<-c(init,bd.2010$inc,fin)
len<-10000
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
bd.2010.ind<-data.frame(s)
names(bd.2010.ind)[1]=c("inc")
bd.2010.ind$inc<-bd.2010.ind$inc/1000
@

@@

par(mfrow=c(1,3))
g10 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of 2003 Distribution")
title(main=paste("Overall realtive density"))
abline(h=1,lty=2)
g1A <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2003 Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2003 Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

<<setup_data>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
library(reldist, quietly=TRUE, warn.conflicts = FALSE)
library(foreign)
# Get Brülhartdata for 2010
estv2010 <- read.csv("../../data/estv_normal_sonder_mitNuller_stE_2010.csv",sep=";")
###########################################
# Select percentiles for all cases (total)
estv2010.total<-estv2010[c(18:38),c(1,4)]
##
# Simulate individual data points
# cumulative probabilites
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
# probabilities
prob<-c(cum.p[1],diff(cum.p), 1-0.9999)
# extreme values beyond x (to sample)
#freq<-max(normal$anz_pflichtige)
freq<-3000
init<-0
fin<-(abs(max(estv2010.total$Total,na.rm=TRUE))+5)
# generate the sequence to take pairs from
ival<-c(init,estv2010.total$Total,fin)
len<-10000 # sequence of each pair
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
estv2010.total.ind<-data.frame(s)
names(estv2010.total.ind)[1]=c("inc")
estv2010.total.ind$inc<-estv2010.total.ind$inc/1000

@@

density1 <- density(habe10$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(-30, 1400),
     ylim=c(0,1.097e-02))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(800,800),y=c(1.097e-02,1.097e-02))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.total.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

estv2010.married<-estv2010[c(18:38),c(1,2)]
names(estv2010.married)[2]=c("married")
##
# Simulate individual data points
# Percentile-Plot (descriptive  purpose)
# cumulative probabilites
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
# probabilities
prob<-c(cum.p[1],diff(cum.p), 1-0.9999)
# extreme values beyond x (to sample)
#freq<-max(normal$anz_pflichtige)
freq<-3000
init<-0
fin<-(abs(max(estv2010.married$married,na.rm=TRUE))+5)
# generate the sequence to take pairs from
ival<-c(init,estv2010.married$married,fin)
len<-10000 # sequence of each pair
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
estv2010.married.ind<-data.frame(s)
names(estv2010.married.ind)[1]=c("inc")
estv2010.married.ind$inc<-estv2010.married.ind$inc/1000

@@

density1 <- density(habe10.married$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(min(rbind(density1$x,density2$x)), max(rbind(density1$x,density2$x))),
     ylim=c(0,max(rbind(density1$y,density2$y))))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(median(rbind(density1$x,density2$x)),median(rbind(density1$x,density2$x))),y=c(max(rbind(density1$y,density2$y)),max(rbind(density1$y,density2$y))))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.married.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

estv2010.unmarried<-estv2010[c(18:38),c(1,3)]
names(estv2010.unmarried)[2]=c("unmarried")
##
# Simulate individual data points
# Percentile-Plot (descriptive  purpose)
# cumulative probabilites
cum.p<-c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,96,97,98,99,99.5,99.9,99.99)/100
# probabilities
prob<-c(cum.p[1],diff(cum.p), 1-0.9999)
# extreme values beyond x (to sample)
#freq<-max(normal$anz_pflichtige)
freq<-3000
init<-0
fin<-(abs(max(estv2010.unmarried$unmarried,na.rm=TRUE))+5)
# generate the sequence to take pairs from
ival<-c(init,estv2010.unmarried$unmarried,fin)
len<-10000 # sequence of each pair
s<-sapply(2:length(ival),function(i){
  seq(ival[i-1],ival[i],length.out=len)
})
s<-sample(s,freq,prob=rep(prob, each=len),replace=T)
estv2010.unmarried.ind<-data.frame(s)
names(estv2010.unmarried.ind)[1]=c("inc")
estv2010.unmarried.ind$inc<-estv2010.unmarried.ind$inc/1000

@@

density1 <- density(habe10.unmarried$inc_habe)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "Einkommen", ylab = "density",
     axes = FALSE,
     xlim = c(min(rbind(density1$x,density2$x)), max(rbind(density1$x,density2$x))),
     ylim=c(0,max(rbind(density1$y,density2$y))))
title(main="FTA vs HBS income distribution",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(median(rbind(density1$x,density2$x)),median(rbind(density1$x,density2$x))),y=c(max(rbind(density1$y,density2$y)),max(rbind(density1$y,density2$y))))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("HBS","FTA"))
density2 <- density(estv2010.unmarried.ind$inc)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

par(mfrow=c(1,3))
g10 <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of HBS Distribution")
title(main=paste("Overall realtive density"))
abline(h=1,lty=2)
g1A <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@
